Cosmological Evidences of Dark Matter through the CMB

### 2019-02-27 paper/main.tex
small mistake

\section{Comments on the results and plots of the CMB spectrum}
We have outlined how we expect matter to behave at large and small scales.
Let us now see if our predictions are compatible with the measured temperature power spectrum.
The behavior of the primordial plasma is imprinted in the CMB photons, in fact, we observe the density fluctuations as anisotropies in the sky map temperature.
In order to relate the fluctuations at different scales and the deviations from the average temperature $2.7$ K on the CMB map, it is necessary to decompose the observed temperature deviation $T(\theta, \phi)$ into a set of orthonormal functions on the sky.
The spherical harmonics $Y^{m} _{l} (\theta, \phi)$ are suitable for this.\\
So if $T(\theta,\phi)$ is the temperature at position $(\theta,\phi)$ on the sky map,
we can write:
\begin{equation}
T(\theta, \phi) = \sum _{l, m} a_{lm} Y^{m} _l (\theta, \phi)
\end{equation}
Due to the orthonormality of the spherical harmonics, we obtain the coefficients:
\begin{equation}
a_{lm} = \int _0 ^{2 \pi} \dd \phi \int _0  ^{\pi} \dd \theta \,
\sin( \theta) \, T(\theta, \phi) \, Y^{m} _l (\theta, \phi)
 \end{equation} 
We define the power spectrum of the temperature map as 
 \begin{equation}
 C_l = \dfrac{1}{2l+1} \sum _{m=-l} ^{l} |a_{lm}|^2
 \end{equation}
The decomposition in spherical harmonics allow us to study the temperature fluctuations at different scales on the sky, smaller is the scale of the fluctuations bigger is the pole $l$.
The poles are inversely proportional to a an angle on the sky, $l \sim 1/ \theta$, for small $l$ we are considering big scales of the sky map, vice versa for big $l$.
As we consider increasing $l$ we are looking at fluctuations in the primordial plasma that have a decreasing  scale and thus a smaller wavelength.\\
The measured temperature power spectrum is shown in Figure(\ref{temp_pow_spect}).
%
%
%
\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{planck2018}
\caption{Planck 2018 temperature power spectrum. $\mathcal{D}^{TT}_l = l(l+1)C_l$ (arXiv:1807.06209v1)}
\label{temp_pow_spect}
\end{figure}
%
%
%
For large scales, small $l<30$, the power spectrum is constant and oscillations do not take place.
Therefore, the Sachs-Wolfe effect is dominant on large scales where the oscillations have too large wavelength to complete an entire oscillations before recombination and, consequently, the power spectrum is almost constant.\\
For large $l$ the acoustic oscillations are dominant.
The first peak is at $l \approx 200$ approximately $1 ^o$ on the sky, it represents how the tiny variations in the fluid density gave rise to a sound wave which collapsed exactly at the time of recombination.
The position of the peak tells us at which scale the first total compression of the primordial plasma happened.
The second peak is linked to those oscillations that compressed and expanded, and they reached the maximal rarefaction of the plasma at recombination.
You might think that the rarefaction should be associated with the local minimum after the first peak, but this is not the case because the power spectrum is sensitive to the absolute value of the temperature oscillations.
The third peak is related to the oscillations that collapsed expanded and re-collapsed, and so on for the higher peaks.\\
Notice that as we consider higher and higher $l$, i.e. smaller scales, the damping effects become relevant, especially for  $l>10^{3}$.\\
The four density parameters $\Omega$ encode the energy-matter content of the Universe and they are constrained by the shape of the CMB power spectrum.
Since the radiation density parameter can be precisely determined by the measurements of the CMB temperature, we analyze how the power spectrum changes if we vary the other  parameters $\Omega_{k 0}$, $\Omega_{\Lambda 0}$ and $\Omega_{m 0}_$.

>>>>

\section{Comments on the results and plots of the CMB spectrum}
We have outlined how we expect matter to behave at large and small scales.
Let us now see if our predictions are compatible with the measured temperature power spectrum.
The behavior of the primordial plasma is imprinted in the CMB photons, in fact, we observe the density fluctuations as anisotropies in the sky map temperature.
In order to relate the fluctuations at different scales and the deviations from the average temperature $2.7$ K on the CMB map, it is necessary to decompose the observed temperature deviation $T(\theta, \phi)$ into a set of orthonormal functions on the sky.
The spherical harmonics $Y^{m} _{l} (\theta, \phi)$ are suitable for this.\\
So if $T(\theta,\phi)$ is the temperature at position $(\theta,\phi)$ on the sky map,
we can write:
\begin{equation}
T(\theta, \phi) = \sum _{l, m} a_{lm} Y^{m} _l (\theta, \phi)
\end{equation}
Due to the orthonormality of the spherical harmonics, we obtain the coefficients:
\begin{equation}
a_{lm} = \int _0 ^{2 \pi} \dd \phi \int _0  ^{\pi} \dd \theta \,
\sin( \theta) \, T(\theta, \phi) \, Y^{m} _l (\theta, \phi)
 \end{equation} 
We define the power spectrum of the temperature map as 
 \begin{equation}
 C_l = \dfrac{1}{2l+1} \sum _{m=-l} ^{l} |a_{lm}|^2
 \end{equation}
The decomposition in spherical harmonics allow us to study the temperature fluctuations at different scales on the sky, smaller is the scale of the fluctuations bigger is the pole $l$.
The poles are inversely proportional to a an angle on the sky, $l \sim 1/ \theta$, for small $l$ we are considering big scales of the sky map, vice versa for big $l$.
As we consider increasing $l$ we are looking at fluctuations in the primordial plasma that have a decreasing  scale and thus a smaller wavelength.\\
The measured temperature power spectrum is shown in Figure(\ref{temp_pow_spect}).
%
%
%
\begin{figure}
\centering
\includegraphics[width=0.9\textwidth]{planck2018}
\caption{Planck 2018 temperature power spectrum. $\mathcal{D}^{TT}_l = l(l+1)C_l$ (arXiv:1807.06209v1)}
\label{temp_pow_spect}
\end{figure}
%
%
%
For large scales, small $l<30$, the power spectrum is constant and oscillations do not take place.
Therefore, the Sachs-Wolfe effect is dominant on large scales where the oscillations have too large wavelength to complete an entire oscillations before recombination and, consequently, the power spectrum is almost constant.\\
For large $l$ the acoustic oscillations are dominant.
The first peak is at $l \approx 200$ approximately $1 ^o$ on the sky, it represents how the tiny variations in the fluid density gave rise to a sound wave which collapsed exactly at the time of recombination.
The position of the peak tells us at which scale the first total compression of the primordial plasma happened.
The second peak is linked to those oscillations that compressed and expanded, and they reached the maximal rarefaction of the plasma at recombination.
You might think that the rarefaction should be associated with the local minimum after the first peak, but this is not the case because the power spectrum is sensitive to the absolute value of the temperature oscillations.
The third peak is related to the oscillations that collapsed expanded and re-collapsed, and so on for the higher peaks.\\
Notice that as we consider higher and higher $l$, i.e. smaller scales, the damping effects become relevant, especially for  $l>10^{3}$.\\
The four density parameters $\Omega$ encode the energy-matter content of the Universe and they are constrained by the shape of the CMB power spectrum.
Since the radiation density parameter can be precisely determined by the measurements of the CMB temperature, we analyze how the power spectrum changes if we vary the other  parameters $\Omega _{k 0}$, $\Omega _{\Lambda 0}$ and $\Omega _{m 0}$.
